Large and Infinitary Quotient Inductive-Inductive Types

### 2020-01-10 draft/paper.tex
paper
\U instead of U
missing word

Following \cite{kaposi2019constructing}, we do this by creating a model of ToS,
where contexts are categories supporting the above requirements and
substitutions are appropriate structure-preserving functors. Then, each
signature can applied to this model, yielding an interpretation of the signature
as a structured category of algebras.

@@

\section{Conclusions and further work}
\label{sec:conclusion}

@@

With regards to the expressiveness of QIIT signatures, we do not yet
support sort equations, i.e. equations of elements of $\Tm\,\Gamma\,U$ in
signatures. Sort equations are included in Cartmell's generalized algebraic
theories \cite{gat}, and they appear to be highly useful for giving an algebraic
representation for Russell-style universes and cumulative universes
\cite{sterling2019algebraic}. We leave this for future work, but we note that
the current isofibration-based semantics does not work in the presence of strict
sort equations, since they are not invariant under isomorphism; instead, sort
equations are compatible with the stricter semantics of
\cite{kaposi2019constructing}.

>>>>

Following \cite{kaposi2019constructing}, we do this by creating a model of ToS,
where contexts are categories supporting the above requirements and
substitutions are appropriate structure-preserving functors. Then, each
signature can be applied to this model, yielding an interpretation of the signature
as a structured category of algebras.

@@

\section{Conclusions and Further Work}
\label{sec:conclusion}

@@

With regards to the expressiveness of QIIT signatures, we do not yet
support sort equations, i.e. equations of elements of $\Tm\,\Gamma\,\U$ in
signatures. Sort equations are included in Cartmell's generalized algebraic
theories \cite{gat}, and they appear to be highly useful for giving an algebraic
representation for Russell-style universes and cumulative universes
\cite{sterling2019algebraic}. We leave this for future work, but we note that
the current isofibration-based semantics does not work in the presence of strict
sort equations, since they are not invariant under isomorphism; instead, sort
equations are compatible with the stricter semantics of
\cite{kaposi2019constructing}.
